---
title: "Moral Anger or Disgust First? Exploring the Primacy Effect in Victim and Perpetrator Foci"
subtitle: "Eva L. Vives, Astrid Thébault Guiochon, Bastien Trémolière, Agnès Falco, Hakim Djeriouat"
author: "<i>Script: Astrid Thébault Guiochon & Eva L. Vives</i>"
output: 
  html_document: 
    toc: yes
    toc_float: yes
    toc_depth: 4
    theme: lumen
    highlight: kate
tags: [knitr, servr]
---

```{r setup, include = FALSE}
options(knitr.kable.NA = '', knitr.table.format = "html")
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 
```

# I -- Loading

## 1. Librairies

```{CRAN, include = FALSE}
if (!require("aod")) 
  install.packages("aod")
if (!require("broom.mixed")) 
  install.packages("broom.mixed")
if (!require("car")) 
  install.packages("car")
if (!require("data.table")) 
  install.packages("data.table")
if (!require("dplyr")) 
  install.packages("dplyr")
if (!require("effects")) 
  install.packages("effects")
if (!require("emmeans")) 
  install.packages("emmeans")
if (!require("fitdistrplus")) 
  install.packages("fitdistrplus")
if (!require("ggeffects")) 
  install.packages("ggeffects")
if (!require("ggplot2")) 
  install.packages("ggplot2")
if (!require("ggpubr")) 
  install.packages("ggpubr")
if (!require("ggthemes")) 
  install.packages("ggthemes")
if (!require("gridExtra")) 
  install.packages("gridExtra")
if (!require("knitr")) 
  install.packages("knitr")
if (!require("labelled")) 
  install.packages("labelled")
if (!require("lme4")) 
  install.packages("lme4")
if (!require("lmerTest")) 
  install.packages("lmerTest")
if (!require("lmtest")) 
  install.packages("lmtest")
if (!require("magrittr")) 
  install.packages("magrittr")
if (!require("MuMIn")) 
  install.packages("MuMIn")
if (!require("nortest")) 
  install.packages("nortest")
if (!require("performance")) 
  install.packages("performance")
if (!require("plyr")) 
  install.packages("plyr")
if (!require("plotly")) 
  install.packages("plotly")
if (!require("readr")) 
  install.packages("readr")
if (!require("readxl")) 
  install.packages("readxl")
if (!require("sjPlot")) 
  install.packages("sjPlot")
if (!require("tidyr")) 
  install.packages("tidyr")
if (!require("tidyverse")) 
  install.packages("tidyverse")
if (!require("tinytex")) 
  tinytex::install_tinytex()
remotes::install_github("mattansb/ggggeffects")
```

```{r libraries}
library(aod)
library(broom.mixed)
library(car)
library(data.table)
library(dplyr)
library(effects)
library(emmeans)
library(fitdistrplus)
library(ggeffects)
library(ggplot2)
library(ggpubr)
library(ggthemes)
library(gridExtra)
library(gtsummary)
library(labelled)
library(lme4)
library(lmerTest)
library(lmtest)
library(magrittr)
library(MuMIn)
library(nortest)
library(performance)
library(plyr)
library(plotly)
library(readr)
library(readxl)
library(sjPlot)
library(tidyr)
source('./ggplot_theme_Publication-2.R')
```

## 2. Working directory

⚠️ Adapt to your computer

```{r directory, include = FALSE}
# Eva
# data = read.csv("~/Moralem/Study 1/Dataset_s1_final_221223.csv", sep = ";", header = T, dec = ".", na.strings = "NA")
# data2 = read.csv("~/Moralem/Study 2/Dataset_s2_final_181223.csv", sep = ";", header = T, dec = ".", na.strings = "NA")
```

## 3. Dataset

💡 Opens an explorer window (or use file path)

```{r data, include = FALSE}
# Dataset study 1
data = read.csv("./Dataset_s1.csv", sep = ";", header = T, dec = ".", na.strings = "NA")
#f = file.choose()
#data = read.csv(f, sep = ";", header = T, dec = ".", na.strings = "NA")

# Dataset study 2
data2 = read.csv("./Dataset_s2.csv", sep = ";", header = T, dec = ".", na.strings = "NA")
#f = file.choose()
#data2 = read.csv(f, sep = ";", header = T, dec = ".", na.strings = "NA")
#rm(f)
```

```{r data-prep-labels, include = FALSE, warnings = FALSE}
var_label(data) = list(condition = "Condition (Appraisal)",
                       newemo = "Emotion",
                       newclass = "Class of Transgression",
                       age = "Age",
                       newgender = "Sex",
                       political_orientation = "Political Orientation (1-Liberal to 7-Conservative")

data = 
  data |>
  mutate(across(c(condition, newgender, newemo, newclass, political_orientation), as.factor)) |>
  mutate(condition = recode(condition, 
                            Agresseur = "Perpetrator", 
                            Victime = "Victim"),
         newgender = recode(newgender, 
                            "0" = "Female", 
                            "1" = "Male"),
         newemo = recode(newemo, 
                         colere = "Anger", 
                         degout = "Disgust", 
                         joie = "Joy", 
                         neutre = "Neutral",
                         peur = "Fear", 
                         tristesse = "Sadness"),
         newclass = recode(newclass, 
                           abandonment = "Abandonment", 
                           betrayal = "Betrayal", 
                           harm = "Harm",
                           humiliation = "Humiliation", 
                           injustice = "Injustice")) |>
  rename(item = newslide)

var_label(data2) = list(condition = "Condition (Appraisal)",
                        newemo = "Emotion",
                        newclass = "Class of Transgression",
                        scenarios = "Scenario",
                        age = "Age",
                        newgender = "Sex",
                        political_orientation = "Political Orientation (1-Liberal to 7-Conservative")

data2 = 
  data2 |>
  mutate(across(c(condition, newgender, newemo, newclass, political_orientation, scenarios), as.factor)) |>
  mutate(condition = recode(condition, 
                            Agresseur = "Perpetrator", 
                            Victime = "Victim"),
         newgender = recode(newgender, 
                            "0" = "Female", 
                            "1" = "Male"),
         newemo = recode(newemo, 
                         colere = "Anger", 
                         degout = "Disgust", 
                         neutre = "Neutral",
                         tristesse = "Sadness"),
         newclass = recode(newclass, 
                           harm = "Harm",
                           humiliation = "Humiliation", 
                           injustice = "Injustice",
                           norm = "Control"),
         scenarios = recode(scenarios,
                            moral = "Transgression",
                            norm = "Control"))
  #rename(item = newslide)
```

# II -- Preview

## 1. Demographics

### a) Study 1

```{r demographics1}
summary_data = data[,] %>%
  select(prolific_ID, age, political_orientation, genre) %>%
  group_by(prolific_ID) %>%
  summarise(
    age = first(age),
    political_orientation = first(political_orientation),
    genre = first(genre),
    .groups = 'drop')

summary(summary_data)
count(summary_data$genre)
```


### b) Study 2

```{r demographics2}
summary_data2 = data2[,] %>%
  select(prolific_ID, age, political_orientation, genre) %>%
  group_by(prolific_ID) %>%
  summarise(
    age = first(age),
    political_orientation = first(political_orientation),
    genre = first(genre),
    .groups = 'drop')

summary_data2
count(summary_data2$genre)
```

## 2. Distribution of reaction time

### a) Study 1

```{r plot-rt1}
fit_norm = fitdist(as.numeric(na.exclude(data$rt_net)), distr = "norm")
#shapiro.test(data$rt_net)
ad.test(data$rt_net) #Anderson Darling as shapiro test has a samplz size max
fit_log = fitdist(as.numeric(log((na.exclude(data$rt_net)))), distr = "norm")

plot(fit_norm)
plot(fit_log)
```

### b) Study 2

```{r plot-rt2}
fit_norm2 = fitdist(as.numeric(na.exclude(data2$rt_net)), distr = "norm")
#shapiro.test(data2$rt_net)
ad.test(data2$rt_net) #Anderson Darling as shapiro test has a samplz size max
fit_log2 = fitdist(as.numeric(log((na.exclude(data2$rt_net)))), distr = "norm")

plot(fit_norm2)
plot(fit_log2)
```

# III -- Models

## 1. Study 1

### a) Reaction Time

#### Full mixed-effect model

```{r s1-rt-lmer, results = 'hide'}
full = lmer(log(rt_net) ~ condition * newemo + (1|number_ID) + (1|item), 
           na.action = na.omit, 
           data = data)
```

Summary

```{r s1-rt-lmer-show}
tbl_regression(full, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-rt-lmer-info}
Anova(full, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(full, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(5) =  120.998, p < .001$$ 
- Interaction between <i>Condition</i> and <i>Emotion</i> $$\chi^2(5) = 23.82, p < .001$$ 

Variance explained by the model: 
$$R^2_m = 0.98\% \text{ (fixed)}$$
$$R^2_c = 43.93\% \text{ (fixed + random)}$$

#### Pairwise comparisons & estimated marginal means

```{r s1-rt-lmer-cont}
emmeans(full, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full, pairwise ~ condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

#### Plot all interaction effects

```{r s1-rt-lmer-plot}
plotfull = ggpredict(full, terms = c("newemo", "condition"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Reaction Time (ms)", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(800, 850, 900, 950, 1000, 1050, 1100, 1150))
  
plotfull
```

### b) Emotional Hits

#### Full generalized mixed-effect model

```{r s1-hit-lmer, results = 'hide'}
emo = glmer(score ~ newemo * condition + (1|number_ID) + (1|item),
          data = data, 
          family = binomial, 
          na.action = na.omit, 
          control = glmerControl(optimizer = "bobyqa"))
```

Summary

```{r s1-hit-lmer-show}
tbl_regression(emo, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-hit-lmer-info}
Anova(emo, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(emo, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(5) = 264.81, p < .001$$
- Interaction between <i>Condition</i> and <i>Emotion</i> $$\chi^2(5) = 145.645, p < .001$$ 

Variance explained by the model:
$$R^2_m = 4.40\% \text{ (fixed)}$$
$$R^2_c = 35.74\% \text{ (fixed + random)}$$

#### Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s1-hit-lmer-cont}
emmeans(emo, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo, pairwise ~ condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

#### Plot all interaction effects

```{r s1-hit-lmer-plot}
plotemo = ggpredict(emo, terms = c("newemo", "condition"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Emotional Hits", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1))

plotemo
```

### c) Exploratory Analyses

#### Full mixed-effect model with condition

```{r s1-exp1-lmer, results = 'hide'}
class = lmer(log(rt_net) ~ condition * newclass * newemo + (1|number_ID) + (1|item), 
             na.action = na.omit, 
             data = data)
```

Summary

```{r s1-exp1-lmer-show}
tbl_regression(class, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion",
                            newclass ~ "Class of Trangression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```   

Anova & conditional and marginal coefficient of determination

```{r s1-exp1-lmer-info}
Anova(class, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(class, method = "marginal"), 4)
```
- Main effect of <i>Emotion</i> $$\chi^2(5) = 11.8516, p = .037$$ 

Variance explained by the model:
$$R^2_m = 1.2\% \text{ (fixed)}$$
$$R^2_c = 44.07\% \text{ (fixed + random)}$$ 

Pairwise comparisons & estimated marginal means

```{r s1-exp1-lmer-cont}
emmeans(class, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s1-exp1-lmer-plot}
plotclass = ggpredict(class, terms = c("newemo"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Reaction Time (ms)", colour = "Emotion", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication()

plotclass
```

#### Full mixed-effect model without condition

```{r s1-exp2-lmer, results = 'hide'}
class2 = lmer(log(rt_net) ~ newclass * newemo + (1|number_ID) + (1|item), 
              na.action = na.omit, 
              data = data)
summary(class2)
```

Summary

```{r s1-exp2-lmer-show}
tbl_regression(class2, 
               label = list(newemo ~ "Emotion",
                            newclass ~ "Class of Trangression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-exp2-lmer-info}
Anova(class2, type = 3)
round(r.squaredGLMM(class2, method = "marginal"), 4)
```
- Main effect of <i>Emotion</i> $$\chi^2(5) = 43.6176, p < .001$$ 
- Interaction between <i>CLass</i> and <i>Emotion</i> $$\chi^2(20) = 43.6176, p < .001$$ 

Variance explained by the model:
$$R^2_m = 0.99\% \text{ (fixed)}$$
$$R^2_c = 43.83\% \text{ (fixed + random)}$$

#### Difference between the two models

```{r s1-exp1-2-lmer-comp}
anova(class, class2) 
lrtest(class2, class)
```

- No significant difference between the 2 (ANOVA)
- Model with condition better than the one without: $$X^2(30) = 113.5, p < .001$$

#### RT with Condition and Class (preregistered)

```{r s1-exp3-rt-lmer}
exprt1 = lmer(log(rt_net) ~ condition * newclass + (1|number_ID) + (1|item), 
           na.action = na.omit, 
           data = data)
```

Summary

```{r s1-exp3-rt-lmer-show}
tbl_regression(exprt1, 
               label = list(condition ~ "Condition",
                            newclass ~ "Class of Trangression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-exp3-rt-lmer-info}
Anova(exprt1, type = 3)
round(r.squaredGLMM(exprt1, method = "marginal"), 4)
```

No significant effect

Variance explained by the model:
$$R^2_m = 0.14\% \text{ (fixed)}$$
$$R^2_c = 43.00\% \text{ (fixed + random)}$$

#### Emotional Hits with Condition and Class (preregistered)

```{r s1-exp3-hit-lmer}
exphit1 = glmer(score ~ condition * newclass + (1|number_ID) + (1|item),
          na.action = na.omit, 
          data = data, 
          family = binomial,
          control = glmerControl(optimizer = "bobyqa"))
```

Summary

```{r s1-exp3-hit-lmer-show}
tbl_regression(exphit1, 
               label = list(condition ~ "Condition",
                            newclass ~ "Class of Transgression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-exp3-hit-lmer-info}
Anova(exphit1, type = 3)
round(r.squaredGLMM(exphit1, method = "marginal"), 4)
```

- Main effect of <i>Class</i> $$\chi^2(4) = 20.194, p < .001$$ 

Variance explained by the model:
$$R^2_m = 0.69\% \text{ (fixed)}$$
$$R^2_c = 30.83\% \text{ (fixed + random)}$$

Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s1-exp3-hit-lmer-cont}
emmeans(exphit1, pairwise ~ newclass, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s1-exp3-hit-lmer-plot}
plotexphit1 = ggpredict(exphit1, terms = c("newclass"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Class of Transgression", y = "Emotional Hits", colour = "Class of Transgression", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1))

plotexphit1
```

#### RT with Condition and Class + covariates (preregistered)

Full mixed-effect model

```{r s1-exp4-rt-lmer, results = 'hide'}
fullcov = lmer(log(rt_net) ~ condition * newemo + age + newgender + political_orientation + (1|number_ID) + (1|item), 
           na.action = na.omit, 
           data = data)
```

Summary

```{r s1-exp4-rt-lmer-show}
tbl_regression(fullcov, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion",
                            age ~ "Age",
                            newgender ~ "Sex",
                            political_orientation ~ "Political Orientation (1-Liberal to 7-Conservative)")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-exp4-rt-lmer-info}
Anova(fullcov, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(fullcov, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(5) = 117.204, p < .001$$ 
- Interaction of <i>Emotion</i> and <i>Condition</i> $$\chi^2(5) = 23.854, p < .001$$ 

Variance explained by the model:
$$R^2_m = 2.77\% \text{ (fixed)}$$
$$R^2_c = 45.24\% \text{ (fixed)}$$

Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s1-exp4-rt-lmer-cont}
emmeans(fullcov, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(fullcov, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s1-exp4-rt-lmer-plot}
plotfullcov = ggpredict(fullcov, terms = c("newemo", "condition"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Reaction Time (ms)", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(800, 850, 900, 950, 1000, 1050, 1100, 1150, 1200, 1250))

plotfullcov
```

#### Emotional Hits with Condition and Class + covariates (preregistered)

Full mixed-effect model

```{r s1-exp4-hit-lmer, results = 'hide'}
emocov = glmer(score ~ newemo * condition + age + newgender + political_orientation + (1|number_ID) + (1|item),
          data = data, 
          family = binomial, 
          na.action = na.omit, 
          control = glmerControl(optimizer = "bobyqa"))
```

Summary

```{r s1-exp4-hit-lmer-show}
tbl_regression(emocov, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion",
                            age ~ "Age",
                            newgender ~ "Sex",
                            political_orientation ~ "Political Orientation (1-Liberal to 7-Conservative)")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s1-exp4-hit-lmer-info}
Anova(emocov, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(emocov, method = "marginal"), 4)
```
- Main effect of <i>Emotion</i> $$\chi^2(5) = 265.849, p < .001$$ 
- Main effect of <i>Age</i> $$\chi^2(1) = 5.378, p = .020$$ 
- Interaction of <i>Emotion</i> and <i>Condition</i> $$\chi^2(5) = 149.011, p < .001$$ 

Variance explained by the model:
$$R^2_m = 7.16\% \text{ (fixed)}$$
$$R^2_c = 35.59\% \text{ (fixed + random)}$$

Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s1-exp4-hit-lmer-cont}
emmeans(emocov, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emocov, pairwise ~ condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emocov, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s1-exp4-hit-lmer-plot}
plotemocov = ggpredict(emocov, terms = c("age", "condition", "newemo"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Age", y = "Emotional Hits", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_x_continuous(breaks = c(20, 30, 40, 50, 60, 70)) +
  scale_y_continuous(breaks = c(0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1))

plotemocov
```

## 2. Study 2

### a) Reaction Time

#### Full mixed-effect model

```{r s2-rt-lmer, results = 'hide'}
full2 = lmer(log(rt_net) ~ condition * newemo * scenarios + (1|number_ID) + (1|item), 
             na.action = na.omit, 
             data = data2)
```

Summary

```{r s2-rt-lmer-show}
tbl_regression(full2, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion",
                            scenarios ~ "Scenario")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Conditional and marginal coefficient of determination

```{r s2-rt-lmer-info}
Anova(full2, type = 3)
round(r.squaredGLMM(full2, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(3) = 58.033, p < .001$$ 
- Interaction of <i>Condition</i> and <i>Emotion</i> $$\chi^2(3) = 8.263, p = .041$$ 
- Interaction of <i>Emotion</i> and <i>Scenario</i> $$\chi^2(3) = 13.005, p = .005$$ 

Variance explained by the model:
$$R^2_m = 1.55\% \text{ (fixed)}$$
$$R^2_c = 33.90\% \text{ (fixed + random)}$$

#### Pairwise comparisons & estimated marginal means

```{r s2-rt-lmer-cont}
emmeans(full2, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full2, pairwise ~ scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full2, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full2, pairwise ~ newemo|scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full2, pairwise ~ scenarios|newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni") 
```

#### Plot all interaction effects

```{r s2-rt-lmer-plot}
plotfull2 = ggpredict(full2, terms = c("scenarios", "condition", "newemo"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Scenario", y = "Reaction Time (ms)", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(800, 850, 900, 950, 1000, 1050, 1100, 1150, 1200, 1250, 1300, 1350, 1400))

plotfull2
```

### b) Emotional Hits

#### Full generalized mixed-effect model

```{r s2-hit-lmer, results = 'hide'}
emo2 = glmer(score ~ scenarios * newemo * condition + (1|number_ID) + (1|item),
             data = data2, 
             family = binomial,
             control = glmerControl(optimizer = "bobyqa"))
```

Summary

```{r s2-hit-lmer-show}
tbl_regression(emo2, 
               label = list(condition ~ "Condition",
                            newemo ~ "Emotion",
                            scenarios ~ "Scenario")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s2-hit-lmer-info}
Anova(emo2, type = 3)
round(r.squaredGLMM(emo2, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(3) = 28.663, p < .001$$ 
- Interaction between <i>Emotion</i> and <i>Scenario</i> $$\chi^2(3) = 46.567, p < .001$$ 
- Interaction between <i>Emotion</i> and <i>Condition</i> $$\chi^2(3) = 25.566, p < .001$$ 
- Interaction between <i>Emotion</i>, <i>Condition</i> and <i>Scenario</i> $$\chi^2(3) = 10.004, p = .019$$ 

Variance explained by the model:
$$R^2_m = 1.86\% \text{ (fixed)}$$
$$R^2_c = 22.64\% \text{ (fixed + random)}$$

#### Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s2-hit-lmer-cont}
emmeans(emo2, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2, pairwise ~ scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2, pairwise ~ newemo|scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2, pairwise ~ scenarios|newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni") 
emmeans(emo2, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2, pairwise ~ scenarios*condition*newemo, type = "response", adjust = "bonferroni")
```

#### Plot all interaction effects

```{r s2-hit-lmer-plot}
plotemo2 = ggpredict(emo2, terms = c("newemo", "condition", "scenarios"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Emotional Hits", colour = "Condition", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1))

plotemo2
```

### c) Exploratory Analyses

Preparation

```{r s2-exp1-prep}
subdata = data2 %>%
  filter(newclass %in% c("Harm", "Injustice", "Humiliation"))
```

#### RT with Condition and Class (preregistered)

```{r s2-exp1-rt-lmer}
exprt2 = lmer(log(rt_net) ~ condition * newclass + (1|number_ID) + (1|item),
              na.action = na.omit, 
              data = subdata)
```

Summary

```{r s2-exp1-rt-lmer-show}
tbl_regression(exprt2, 
               label = list(condition ~ "Condition",
                            newclass ~ "Class of Transgression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s2-exp1-rt-lmer-info}
Anova(exprt2, type = 3)
round(r.squaredGLMM(exprt2, method = "marginal"), 4)
```

- Main effect of <i>Class</i> $$\chi^2(2) = 11.381, p = .003$$ 

Variance explained by the model:
$$R^2_m = 1.15\% \text{ (fixed)}$$
$$R^2_c = 34.58\% \text{ (fixed + random)}$$

Pairwise comparisons & estimated marginal means

```{r s2-exp1-rt-lmer-cont}
emmeans(exprt2, pairwise ~ newclass, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s2-exp1-rt-lmer-plot}
plotexprt2 = ggpredict(exprt2, terms = c("newclass"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Class of Trangression", y = "Reaction Time (ms)", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication()

plotexprt2
```

#### Emotional Hits with Condition and Class (preregistered)

```{r s2-exp1-hit-lmer}
exphit2 = glmer(score ~ condition * newclass + (1|number_ID) + (1|item),
             data = subdata, 
             family = binomial,
             control = glmerControl(optimizer = "bobyqa"))
```

Summary

```{r s2-exp1-hit-lmer-show}
tbl_regression(exphit2, 
               label = list(condition ~ "Condition",
                            newclass ~ "Class of Transgression")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s2-exp1-hit-lmer-info}
Anova(exphit2, type = 3)
round(r.squaredGLMM(exphit2, method = "marginal"), 4)
```

- Main effect of <i>Class</i> $$\chi^2(2) = 30.594, p < .001$$ 

Variance explained by the model:
$$R^2_m = 0.017\% \text{ (fixed)}$$
$$R^2_c = 25.98\% \text{ (fixed + random)}$$

Pairwise comparisons & estimated marginal means

```{r s2-exp1-hit-lmer-cont}
emmeans(exphit2, pairwise ~ newclass, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s2-exp1-hit-lmer-plot}
plotexphit2 = ggpredict(exphit2, terms = c("newclass"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Class of Trangression", y = "Emotional Hits", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1))

plotexphit2
```

#### RT with Condition, Emotion and Class + covariates (preregistered)

Full mixed-effect model

```{r s2-exp2-rt-lmer, results = 'hide'}
full2cov = lmer(log(rt_net) ~ condition * newemo * scenarios + age + newgender + political_orientation + (1|number_ID) + (1|item), 
           na.action = na.omit, 
           data = data2)
```

Summary

```{r s2-exp2-rt-lmer-show}
tbl_regression(full2cov, 
               label = list(condition ~ "Condition",
                            scenarios ~ "Scenarios",
                            newemo ~ "Emotion",
                            age ~ "Age",
                            newgender ~ "Sex",
                            political_orientation ~ "Political Orientation (1-Liberal to 7-Conservative)")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s2-exp2-rt-lmer-info}
Anova(full2cov, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(full2cov, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(3) = 58.017, p < .001$$
- Main effect of <i>Age</i> $$\chi^2(1) = 8.22, p = .004$$
- Interaction of <i>Emotion</i> and <i>Scenario</i> $$\chi^2(3) = 13.021, p = .0045 $$

Variance explained by the model:
$$R^2_m = 5.01\% \text{ (fixed)}$$
$$R^2_c = 35.03\% \text{ (fixed + random)}$$
Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s2-exp2-rt-lmer-cont}
emmeans(full2cov, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(full2cov, pairwise ~ scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s2-exp2-rt-lmer-plot}
plotfull2cov = ggpredict(full2cov, terms = c("age", "scenarios", "newemo"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Age", y = "Reaction Time (ms)", colour = "Scenario", title = "", element_text(size = 14)) +
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_x_continuous(breaks = c(15, 20, 25, 30, 35, 40, 45, 50, 55, 60, 65, 70, 75)) + 
  scale_y_continuous(breaks = c(800, 900, 1000, 1100, 1200, 1300, 1400, 1500, 1600, 1700))
plotfull2cov
```

#### Emotional Hits with Condition, Emotion and Class + covariates (preregistered)

Full mixed-effect model

```{r s2-exp2-hit-lmer, results = 'hide'}
emo2cov = glmer(score ~  condition * newemo * scenarios + age + newgender + political_orientation + (1|number_ID) + (1|item),
          data = data2, 
          family = binomial, 
          na.action = na.omit, 
          control = glmerControl(optimizer = "bobyqa"))
```


Summary

```{r s2-exp2-hit-lmer-show}
tbl_regression(full2cov, 
               label = list(condition ~ "Condition",
                            scenarios ~ "Scenarios",
                            newemo ~ "Emotion",
                            age ~ "Age",
                            newgender ~ "Sex",
                            political_orientation ~ "Political Orientation (1-Liberal to 7-Conservative)")) %>%
  modify_column_unhide(column = std.error) %>%
  modify_column_unhide(column = statistic) %>%
  modify_header(label = "**Variable**") %>% 
  bold_p() %>% 
  modify_fmt_fun(statistic ~ style_sigfig) %>% 
  add_significance_stars(hide_ci = FALSE, 
                         hide_p = FALSE,
                         pattern = "{p.value}{stars}") %>%
  add_glance_source_note(label = list(sigma ~ "\U03C3"),
                         include = c(AIC, sigma))
```

Anova & conditional and marginal coefficient of determination

```{r s2-exp2-hit-lmer-info}
Anova(emo2cov, type = 3, ddf = "Satterthwaite")
round(r.squaredGLMM(emo2cov, method = "marginal"), 4)
```

- Main effect of <i>Emotion</i> $$\chi^2(3) = 28.558, p < .001$$
- Interaction between <i>Emotion</i> and <i>Condition</i> $$\chi^2(3) = 25.494, p < .001$$
- Interaction between <i>Emotion</i> and <i>Scenarios</i> $$\chi^2(3) = 46.448, p < .001$$
- Interaction between <i>Emotion</i>, <i>Condition</i> and <i>Scenarios</i> $$\chi^2(3) = 9.942, p = .019$$

Variance explained by the model:
$$R^2_m = 2.88\% \text{ (fixed)}$$
$$R^2_c = 22.59\% \text{ (fixed + random)}$$
Pairwise comparisons (estimated marginal means and pairwise comparisons)

```{r s2-exp2-hit-lmer-cont}
emmeans(emo2cov, pairwise ~ newemo, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2cov, pairwise ~ newemo|condition, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2cov, pairwise ~ newemo|scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
emmeans(emo2cov, pairwise ~ condition*newemo*scenarios, lmer.df = "asymp", type = "response", adjust = "bonferroni")
```

Plot all interaction effects

```{r s2-exp2-hit-lmer-plot}
plotemo2cov = ggpredict(emo2cov, terms = c("newemo", "condition", "scenarios"), ci_level = 0.95) %>% 
  plot() +
  labs(x = "Emotion", y = "Emotional Hits", colour = "Condition", title = "", element_text(size = 14)) + 
  scale_fill_Publication() + 
  scale_colour_Publication() +
  theme_Publication() + 
  scale_y_continuous(breaks = c(0.6, 0.65, 0.7, 0.75, 0.8, 0.85, 0.9, 0.95, 1))

plotemo2cov
```